Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-02-18 RR_manuscript/Draft_RR.Rmd
:memo: - add reviewer ratings in factor analysis

<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats? if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->
At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
<!-- TR: I have a hunch that finding reviewers will potentially be more difficult than finding analysis teams. They had as many reviewers as they had teams.-->
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set.
<!-- TODO: add link to peer review survey -->
The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts: <!-- TR:Need flow chart here-->

@@

- *Measure of uniqueness* [numeric] of individual analyses for the set of predictors in each model ($uniq_i$).
- *Measure of conservativeness* [numeric] of the model specification, as the number of random/group-level effects included ($cons_i$).
- *Number of post-hoc changes to the acoustic measurements* [numeric] the teams will report to have carried out ($phoc_i$).
- *Number of models* [numeric] the teams will report to have run ($modn_i$).
- *Major dimension* [categorical] that has been measured to answer the research question ($mdim_i$).
- *Temporal window* [categorical] that the measurement is taken over ($twin_i$).
- *Data exclusion*, [categorical] whether data has been excluded or not ($excl_i$).

@@

The major measurement dimension of each analysis will be categorized according to the following possible groups: *duration*, *amplitude*, *fundamental frequency*, *other spectral properties* (e.g. frequency center of gravity, harmonics difference, etc.), *other measures* (e.g. principal components, vowel dispersion, etc.)
<!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
<!-- SC: I just added a "other measures" category for other things that are not strictly acoustic. -->
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: *segment*, *syllable*, *word*, *phrase*.

>>>>

<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats? if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->
At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
<!-- TR: I have a hunch that finding reviewers will potentially be more difficult than finding analysis teams. They had as many reviewers as they had teams.-->
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set.
<!-- TODO: add link to peer review survey -->
The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on the following criteria: <!-- TR:Need flow chart here-->

@@

- *Measure of uniqueness* [numeric] of individual analyses for the set of predictors in each model ($uniq_i$).
- *Measure of conservativeness* [numeric] of the model specification, as the number of random/group-level effects included ($cons_i$).
- *Number of post-hoc changes to the acoustic measurements* [numeric] the teams will report to have carried out ($phoc_i$).
- *Number of models* [numeric] the teams will report to have run ($modn_i$).
- *Major dimension* [categorical] that has been measured to answer the research question ($mdim_i$).
- *Temporal window* [categorical] that the measurement is taken over ($twin_i$).
- *Data exclusion*, [categorical] whether data has been excluded or not ($excl_i$).
- *Average peer-review rating* [numeric], as the mean of the peer-review ratings for each analysis.

@@

The major measurement dimension of each analysis will be categorized according to the following possible groups: *duration*, *amplitude*, *fundamental frequency*, *other spectral properties* (e.g. frequency center of gravity, harmonics difference, etc.), *other measures* (e.g. principal components, vowel dispersion, etc.)
<!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
<!-- SC: I just added a "other measures" category for other things that are not strictly acoustic. -->
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: *segment*, *syllable*, *word*, *phrase*.
Since each analysis will receive more than one peer-review rating, we will calculate the mean rating and its standard deviation for each.
These will be entered in the model formula with a measurement-error term (`me(mean, sd)` in brms).
